### 2017-06-09 paper/lexicographic.tex

Define a 
(one-dimensional) stochastic process $\{\tilde{X}_k\}_{k=0}^{\infty}$ as 
follows:
$$
\tilde{X}_k(\omega) = \begin{dcases}
0 & \text{if $\omega \not\in D$}\\
B & \text{if $\omega \in D$ and $k<i$ }\\
\vecseq{X}{k}{j}(\omega) & \text{ if $k\geq i$ and $\tilde{\stime}(\omega)>i$ 
}\\
\vecseq{X}{\tilde{\stime}(\omega)}{j}(\omega) & \text{ if $k\geq i$ and 
$\tilde{\stime}(\omega)\leq i$ }.
\end{dcases}
$$

We prove several properties of the process $\{\tilde{X}_k\}_{k=0}^{\infty}$. 
First, for all $k\geq 0$, $\tilde{X}_k(\omega)\geq K$, where $K<0$ is the 
number 
such that $\vec{X}_j(\omega)\geq K$ for all $j$ and $\omega$ (such a number 
exists from the definition of LexRSM). Second, denote by 
%\begin{enumerate}
%\
%\end{itemize}
%\end{enumerate}

>>>>

Define a 
(one-dimensional) stochastic process $\{\tilde{X}_k\}_{k=0}^{\infty}$ as 
follows:
$$
\tilde{X}_k(\omega) = \begin{dcases}
0 & \text{if $\omega \not\in D$}\\
B & \text{if $\omega \in D$ and $k<i$ }\\
\vecseq{X}{k}{j}(\omega) & \text{if $\omega \in D$, $k\geq i$ and 
$\tilde{\stime}(\omega)>i$ 
}\\
\vecseq{X}{\tilde{\stime}(\omega)}{j}(\omega) & \text{if $\omega\in D$, $k\geq 
i$ and 
$\tilde{\stime}(\omega)\leq i$ }.
\end{dcases}
$$

We prove several properties of the process $\{\tilde{X}_k\}_{k=0}^{\infty}$. 
First, for all $k\geq 0$, $\tilde{X}_k(\omega)\geq K$, where $K<0$ is the 
number 
such that $\vec{X}_j(\omega)\geq (K,\dots,K)$ for all $j$ and $\omega$ (such a 
number 
exists from the definition of LexRSM). Second, for any $k\in \Nset_0$ denote by 
$\noofdec_k$ the random variable such that $\noofdec_k(\omega) = |\{i'\in 
\Nset\mid i \leq i' \leq k \text{ and } \levelrank{\omega}{i'}=j\} |$.
We claim 
that for each $k\geq i$ 
it holds 
\begin{equation}
\label{eq:lexrsm-soundness-main}
\E[\tilde{X}_k]\leq B\cdot \probm(D) - \eps\cdot\sum_{\ell=0}^{k-i-1} \probm(D 
\cap \tilde{\stime}\geq k \cap \noofdec_k 
\geq 
\ell).
\end{equation}

The proof of~\eqref{eq:lexrsm-soundness-main} goes by induction on $k$. For 
$k=i$ the sum on the right-hand side is over an empty set of indexes, so the 
inequality immediately follows from the definition of $\tilde{X}_k$. Now assume 
that~\eqref{eq:lexrsm-soundness-main} holds for some $k\geq i$. 
%\begin{enumerate}
%\
%\end{itemize}
%\end{enumerate}
